%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{MUHAMMAD SHOAIB} % Your name
%\address{123 Broadway \\ City, State 12345} % Your address
\address{Prosper, Texas 75078} % Your secondary addess (optional)
%\address{(469)~$\cdot$~988~$\cdot$~1060 \\ muhdchoaib@gmail.com} % Your phone number and email
\address{Phone: \href{tel:+1(469)988-1060}{(469)~$\cdot$~988~$\cdot$~1060 } \\ 
E-mail: \href{mailto:muhdchoaib@gmail.com}{muhdchoaib@gmail.com} \\ 
LinkedIn: \href{https://www.linkedin.com/in/muhammadshoaib-dev/}{linkedin.com/in/muhammadshoaib-dev}} 

\begin{document}
\begin{rSection}{Professional Summary}
Experienced software developer with expertise in full-stack development using Django and TypeScript. Skilled in AWS cloud deployments, CI/CD pipelines, and system optimization. Proven track record in enhancing application performance, developing RESTful microservices, and collaborating with cross-functional teams. \\
\textbf{U.S. citizen, no sponsorship required.}
\end{rSection}



%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}
%------------------------------------------------
\begin{rSubsection}{Magnit Global}{Jan \('23\) -- Present}{Manager Software Development}{Texas}
\item Developed Django and TypeScript applications, increasing user adoption by 25\%.
\item Improved system efficiency by 30\% through new technologies and tools.
\item Maintained 99.9\% uptime deploying applications in AWS using Pulumi (IAAC).
\item Enhanced user experience in collaboration with cross-functional teams.

\end{rSubsection}

%\begin{rSubsection}{}{}{Full Stack Developer}{Oct 2021 -- Jan 2023}
\begin{rSubsectionSameComp}{Full Stack Developer}{Oct \('21\) -- Jan \('23\)}{}{}
\item Developed RESTful microservices with Django, GraphQL, and PostgreSQL.
\item Launched key product features.
\item Supported AWS deployments, ensuring high availability.
\end{rSubsectionSameComp}

%------------------------------------------------
\begin{rSubsection}{Capital One}{Mar \('21\) -- Oct \('21\)}{Sr. Software Engineer}{Texas}
\item Led development of RESTful microservices using Django and PostgreSQL.
\item Reduced deployment times by 40\% with CI/CD pipelines.
\item Developed and managed Docker applications with Kubernetes.
\end{rSubsection}

%------------------------------------------------
\begin{rSubsection}{Optum Healthcare}{Jan \('19\) -- Mar \('21\)}{Sr. Software Developer}{Texas}
\item Enhanced transaction processing speed by 35\% with robust applications.
\item Increased operational efficiency by 20\% with proprietary software.
\item Reduced downtime incidents by 50\% with RabbitMQ.
\end{rSubsection}

%------------------------------------------------
\begin{rSubsection}{Toyota Connected -- Contract}{Jun \('18\) -- Jan \('19\)}{Software Engineer}{Texas}
\item Developed APIs to expose telemetry data, improving data accessibility.
\item Improved data accuracy by 25\% with real-time processing systems.
\end{rSubsection}

%\newpage
%------------------------------------------------
\begin{rSubsection}{JPM Chase \& Co.}{Feb \('18\) -- Jun \('18\)}{Software Engineer}{Texas}
\item Improved service response times by 25\% with RESTful web services.
\item Enhanced system interoperability with API integrations.
\end{rSubsection}
%\newpage
%------------------------------------------------
\begin{rSubsection}{Cisco Systems Inc.}{Mar \('17\) -- Feb \('18\)}{Software Engineer}{California}
\item Contributed to a 20\% increase in network performance with backend software.
\item Reduced manual testing efforts by 50\% with an automation framework.

\end{rSubsection}

%------------------------------------------------
\begin{rSubsection}{Informatica Corp.}{Jun \('15\) -- Mar \('17\)}{Software Engineer}{California}
\item Enhanced customer data management with backend components.
\item Reduced latency by 30\% with improved application performance.
\end{rSubsection}

%------------------------------------------------
%\begin{rSubsection}{Ericsson Inc.}{May 2014 -- Dec 2014}{Intern}{San Jose, CA}
%\item Implemented Border Gateway Protocol (BGP), contributing to network stability and efficiency.
%\item Assisted in the development of network management tools, improving monitoring and control capabilities.
%\end{rSubsection}

\end{rSection}
\newpage
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of Texas at Arlington, USA} \hfill {\em May \('15\)} \\
M.S. in Computer Science | GPA: 4.0/4.0

{\bf University of Engineering \& Technology Lahore, Pakistan} \hfill {\em Jan \('10\)} \\ 
B.S. in Electrical Engineering | Graduated magna cum laude

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex} \vspace{1ex}} l }
Languages &  Python, Java, Javascript, TypeScript \\
Databases & PostgreSQL, MySQL, MongoDB, Oracle \\
Tools & Git, Jenkins, JIRA, Terraform, Pulumi \\ 
Web Technologies & Django, Flask, JavaScript, RESTful, GraphQL \\
Testing & Selenium WebDriver, Pytest, JMeter \\
Cloud & AWS, Kubernetes, Docker \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
%
